---
title: "Daily Google Trends"
author: "Sietse"
date: "1-5-2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this file, I demonstrate how I found the daily Google Trends estimates.

First, we load in the libraries
```{r}
library(gtrendsR)
library(tidyverse)
library(lubridate)
```

Now follows the code to estimate the daily Google Trends popularity.


Bitcoin popularity for IDEX
```{r}
get_daily_gtrendBTCIDEX <- function(keyword =('Bitcoin'), geo = '', from = '2017-10-16', to = '2020-05-04') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendBTCIDEX(keyword = c('Bitcoin'), geo = '', from = '2017-10-16', to = '2020-05-04')
DBitcoinTrendDataBTCIDEXslice <- DailyBitcoinTrendData %>% slice(1:932) 
View(DBitcoinTrendDataBTCIDEXslice)
```

```{r}
write.csv(DBitcoinTrendDataBTCIDEXslice,"DailyTrendBTCIDEX.csv", row.names = FALSE)
```



IDEX popularity for IDEX
```{r}
get_daily_gtrendIDEX <- function(keyword =('IDEX'), geo = '', from = '2017-10-16', to = '2020-05-04') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendIDEX(keyword = c('IDEX'), geo = '', from = '2017-10-16', to = '2020-05-04')
DBitcoinTrendDataBTCIDEXslice <- DailyBitcoinTrendData %>% slice(1:932) 
View(DBitcoinTrendDataBTCIDEXslice)
```

```{r}
write.csv(DBitcoinTrendDataBTCIDEXslice,"DailyTrendIDEXslice.csv", row.names = FALSE)
```



Ethereum popularity for IDEX
```{r}
get_daily_gtrendIDEXETH <- function(keyword =('Ethereum'), geo = '', from = '2017-10-16', to = '2020-05-04') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendIDEXETH(keyword = c('Ethereum'), geo = '', from = '2017-10-16', to = '2020-05-04')
DBitcoinTrendDataIDEXETHslice <- DailyBitcoinTrendData %>% slice(1:932) 

write.csv(DBitcoinTrendDataIDEXETHslice,"DailyTrendIDEXETHslice.csv", row.names = FALSE)
```


Wash trading popularity for IDEX
```{r}
get_daily_gtrendIDEXWT <- function(keyword =('Wash trading'), geo = '', from = '2017-10-16', to = '2020-05-04') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendIDEXWT(keyword = c('Wash trading'), geo = '', from = '2017-10-16', to = '2020-05-04')
DBitcoinTrendDataIDEXWTslice <- DailyBitcoinTrendData %>% slice(1:932) 

write.csv(DBitcoinTrendDataIDEXWTslice,"DailyTrendIDEXWTslice.csv", row.names = FALSE)
```


Files left (.csv):
DailyTrendBTCIDEX.csv
DailyTrendIDEXslice.csv
DailyTrendIDEXETHslice.csv
DailyTrendIDEXWTslice.csv



Cybercrime popularity for IDEX
```{r}
get_daily_gtrendIDEXCypop <- function(keyword =('Cybercrime'), geo = '', from = '2017-10-16', to = '2020-05-04') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendIDEXCypop(keyword = c('Cyber crime'), geo = '', from = '2017-10-16', to = '2020-05-04')
DBitcoinTrendDataIDEXWTslice <- DailyBitcoinTrendData %>% slice(1:932) 

write.csv(DBitcoinTrendDataIDEXWTslice,"DailyTrendIDEXCypopslice.csv", row.names = FALSE)
```


















































EtherDelta

Bitcoin popularity for EtherDelta (2017-02-10 : 2020-05-02)
```{r}
get_daily_gtrendBTCED <- function(keyword =('Bitcoin'), geo = '', from = '2017-02-10', to = '2020-05-02') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendBTCED(keyword = c('Bitcoin'), geo = '', from = '2017-02-10', to = '2020-05-10')
DBitcoinTrendDataBTCEDslice <- DailyBitcoinTrendData %>% slice(1:1178) 
View(DBitcoinTrendDataBTCEDslice)
```

```{r}
write.csv(DBitcoinTrendDataBTCEDslice,"DailyTrendBTCED.csv", row.names = FALSE)
```



EtherDelta popularity for ED (2017-02-10 : 2020-05-02)
```{r}
get_daily_gtrendIDEX <- function(keyword =('EtherDelta'), geo = '', from = '2017-02-10', to = '2020-05-10') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendIDEX(keyword = c('EtherDelta'), geo = '', from = '2017-02-10', to = '2020-05-10')
DBitcoinTrendDataEDslice <- DailyBitcoinTrendData %>% slice(1:1178) 
View(DBitcoinTrendDataEDslice)
```

```{r}
write.csv(DBitcoinTrendDataEDslice,"DailyTrendEDslice.csv", row.names = FALSE)
```



Ethereum popularity for ED (2017-02-10 : 2020-05-02)
```{r}
get_daily_gtrendEDETH <- function(keyword =('Ethereum'), geo = '', from = '2017-02-10', to = '2020-05-10') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendEDETH(keyword = c('Ethereum'), geo = '', from = '2017-02-10', to = '2020-05-10')
DBitcoinTrendDataEDETHslice <- DailyBitcoinTrendData %>% slice(1:1178) 

write.csv(DBitcoinTrendDataEDETHslice,"DailyTrendEDETHslice.csv", row.names = FALSE)
```


Wash trading popularity for ED
```{r}
get_daily_gtrendEDWT <- function(keyword =('Wash trading'), geo = '', from = '2017-02-10', to = '2020-05-10') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendEDWT(keyword = c('Wash trading'), geo = '', from = '2017-02-10', to = '2020-05-10')
DBitcoinTrendDataEDWTslice <- DailyBitcoinTrendData %>% slice(1:1178) 

write.csv(DBitcoinTrendDataEDWTslice,"DailyTrendEDWTslice.csv", row.names = FALSE)
```


Cybercrime popularity for ED
```{r}
get_daily_gtrendEDCypop <- function(keyword =('Cybercrime'), geo = '', from = '2017-02-10', to = '2020-05-10') {
if (ymd(to) >= floor_date(Sys.Date(), 'month')) {
to <- floor_date(ymd(to), 'month') -days(1)

if (to < from) {
stop('Specifying to date in the current month is not allowed')
}
}
  
aggregated_data <- gtrends(keyword = keyword, geo = geo, time = paste(from, to))
  if(is.null(aggregated_data$interest_over_time)) {
    print('There is no data in Google Trends!')
    return()
  }

mult_m <- aggregated_data$interest_over_time %>%
    mutate(hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    group_by(month = floor_date(date, 'month'), keyword) %>%
    summarise(hits = sum(hits)) %>%
    ungroup() %>%
    mutate(ym = format(month, '%Y-%m'),
           mult = hits / max(hits)) %>%
    select(month, ym, keyword, mult) %>%
    as_tibble()

 pm <- tibble(s = seq(ymd(from), ymd(to), by = 'month'), 
               e = seq(ymd(from), ymd(to), by = 'month') + months(1) - days(1))

 raw_trends_m <- tibble()
 
 for (i in seq(1, nrow(pm), 1)) {
    curr <- gtrends(keyword, geo = geo, time = paste(pm$s[i], pm$e[i]))
    if(is.null(curr$interest_over_time)) next
    print(paste('for', pm$s[i], pm$e[i], 'retrieved', count(curr$interest_over_time), 'days of data (all keywords)'))
    raw_trends_m <- rbind(raw_trends_m,
                         curr$interest_over_time)
 }
 
 trend_m <- raw_trends_m %>%
    select(date, keyword, hits) %>%
    mutate(ym = format(date, '%Y-%m'),
           hits = as.integer(ifelse(hits == '<1', '0', hits))) %>%
    as_tibble()
 
 trend_res <- trend_m %>%
    left_join(mult_m) %>%
    mutate(est_hits = hits * mult) %>%
    select(date, keyword, est_hits) %>%
    as_tibble() %>%
    mutate(date = as.Date(date))
  
  return(trend_res)

}
```

```{r}
DailyBitcoinTrendData <- get_daily_gtrendEDCypop(keyword = c('Cyber crime'), geo = '', from = '2017-02-10', to = '2020-05-10')
DBitcoinTrendDataIDEXWTslice <- DailyBitcoinTrendData %>% slice(1:1178) 

write.csv(DBitcoinTrendDataIDEXWTslice,"DailyTrendEDCypopslice.csv", row.names = FALSE)
```


